---
title: "p8105_hw6_ma4197"
author: "Mayuri Albal"
date: "2022-12-02"
output: html_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(rvest)
```

##Problem 1

*Data Loading and Cleaning*
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

*Bootstrap and Plotting Pt 1*
```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```
*Plotting Pt 2*

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

##Problem 2

*Data Loading*
```{r}
twp_data = read_csv(file= "./data/homicide-data.csv") %>%
janitor::clean_names()
```

*Data Cleaning*
```{r}
murder_df=
twp_data %>%
janitor::clean_names() %>% 
mutate(
  state = replace(state, state== "wI", "WI")) %>% 
mutate(
  city_state= paste(city, state, sep= ",")) %>% 
mutate(
  victim_age = as.numeric(victim_age)) %>% 
filter(!city_state %in% c("Dallas,TX","Phoenix,AZ", "Kansas City,MO","Tulsa,AL" )) %>% 
filter(victim_race %in% c("White","Black")) %>% 
mutate(
    resolved = as.numeric(disposition == "Closed by arrest"))

```
*Checks*
```{r}
murder_df %>% 
  group_by(city_state) %>% 
  count(city_state)
```
```{r}
murder_df %>% 
  summarise(victim_age)
```
```{r}
murder_df %>% 
  count(victim_race)
```
*Linear Model*

```{r}
balt_murder_logfit = 
  murder_df %>% 
  filter(city_state == "Baltimore,MD") %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 
```

```{r}
balt_murder_logfit %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```
```{r}
conf= exp(confint(balt_murder_logfit, level= 0.95))
```


Within the city of Baltimore,MD, the odds of solving a homicide case for a male victim is 0.426 times higher than the odds of solving a homicide case for a female victim, adjusting for the victim's sex and race. We are 95% confident that the true odds of solving a homicide case for a male victim within the Baltimore,MD is between 0.3241 and 0.5575.

*All City Pipeline*
```{r}
allcity_murder=
  murder_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    ac_models = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())),
    results = purrr::map(ac_models, broom::tidy, conf.int = TRUE)) %>% 
  select(city_state, results) %>% 
  unnest(cols = results) 
```

```{r}
all_city=
allcity_murder %>% 
  filter(term== "victim_sexMale") %>% 
  mutate(OR = exp(estimate),
         confh= exp(conf.high),
         confl= exp(conf.low)) %>%
  select(city_state, log_OR = estimate, OR, p.value, confl, confh)
```

```{r}
all_city=
all_city %>% 
mutate(city_state= fct_reorder(city_state, OR))
```

*Plotting*

```{r}
ggplot(all_city, aes(x= city_state, y= OR, color=city_state))+
  geom_point()+
  geom_errorbar(aes(ymin=confl, ymax= confh))+
  theme_classic()+ 
  theme(legend.position= "none")+
  ggtitle("Odds Ratio of Resolved Homicide Cases,Comparing Males to Females, in Large US Cities")+
  theme(plot.title = element_text(hjust= 0.5, size=12),
        axis.text.x.bottom = element_text(size= 7, angle= 90))+
    labs(x = "City",
        y= "Odds Ratio")
```
The estimated OR of resolved homicides, comparing male victims and female victims, for each of the 50 largest cities in the US were graphed in order of lowest to highest OR. New York, NY has the lowest OR for resolved cases of male victims compared to female victims, showing the odds of solving homicide cases for male victims compared to female victims is low. Whilst Albuquerque,NM has the highest, this demonstrates higher odds of solving homicide cases for male victims compared to female victims. Each was fitted with a error bar based upon the lowest and highest values from the estimates 95% confidence interval generated for the Odds Ratio.


##Problem 3

*Load and Clean Data*

```{r}
bwt_data = read_csv(file= "./data/birthweight.csv") %>%
janitor::clean_names()
```

```{r}
bwt_data %>% 
tibble

skimr::skim(bwt_data)
```

```{r}
bwt_data=
bwt_data %>% 
mutate(babysex= recode(babysex, 
                 "1"= "Male",
                 "2"= "Female"),
       frace= recode(frace,
                     "1"= "White",
                     "2"= "Black",
                     "3"= "Asian",
                     "4"= "Puerto Rican",
                     "8"= "Other"),
       mrace= recode(mrace,
                     "1"= "White",
                     "2"= "Black",
                     "3"= "Asian",
                     "4"= "Puerto Rican"),
       malform= recode(malform,
                       "0"= "Absent",
                       "1"= "Present"))
skimr::skim(bwt_data)
```
*Description*
For the 'bwt_data' data set, there are 4342 observations and 20 variables. Within this, the variables 'babysex', 'frace', 'mrace', and 'malform' were recoded into their characteristic definitions rather than the numeric values originally assigned. With this, for variable 'frace' and 'mrace' there were no observations coded as 'Unknown', so it was dropped from the data set.

*Linear Modeling*

```{r}
bwt_model= lm(bwt ~ gaweeks, data=bwt_data)
```


```{r}
bwt_data %>% 
ggplot(aes(x=gaweeks, y=bwt))+
  geom_point(alpha= 0.25)
```
*Description*
A typical gestational period is approximately 40 weeks, with any infant born prior to 37 weeks being deemed as a preterm baby. Shorter gestational times are often associated with lower average birth weight of the child, and as a result we will hypothesize that the average birth weight of an infant will be dependent on the gestational period of the pregnancy. This graph above allows us to observe there is a possible positive relationship between the two variables as the shorter the gestational period is, the lower the birth weight is. Additionally, around 40 weeks there are increased observations around the average birth weight range (3000-4000 grams).

*Residual and Prediction Modeling*

```{r}
modelr::add_residuals(bwt_data, bwt_model)
```

```{r}
modelr::add_predictions(bwt_data, bwt_model)
```

```{r}
bwt_data %>% 
  modelr::add_residuals(bwt_model) %>% 
  modelr::add_predictions(bwt_model) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha=0.25)+
  ggtitle("Residual vs. Fitted Values for Birth Weight Model")+
    labs(x = "Fitted",
        y= "Residual")
```

```{r}
bwt_model %>% 
  broom::tidy() %>% 
  knitr::kable()
```

*Comparing Models*

```{r}
bwt_modelme = lm(bwt~ blength + gaweeks, data = bwt_data)
bwt_modeltwi = lm(bwt~ bhead + blength + babysex+ bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bwt_data)
```

```{r}
model_df = 
  crossv_mc(bwt_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

model_df = 
  model_df %>% 
  mutate(
    bwt_model_n   = map(train, ~lm(bwt ~ gaweeks, data = .x))) %>% 
  mutate(
    bwt_modelme_n = map(train, ~lm(bwt ~ blength + gaweeks, data = .x))) %>% 
  mutate(
    rmse_model    = map2_dbl(bwt_model_n, test, ~rmse(model = .x, data = .y)),
    rmse_modelme  = map2_dbl(bwt_modelme_n, test, ~rmse(model = .x, data = .y)))
```

```{r}
model_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()+
  ggtitle("Comparison of RMSE Values for Birth Weight Models")+
    labs(x = "Model",
        y= "RMSE")
```

*Description*
RMSE was utilized to compare each of the three models due to it allowing for us to measure how far predicted values are from the observed values in a regression. With this, the larger the RMSE is, demonstrates a bigger difference between the predicted and observed values. As a result, it determines whether or not the regression is a good fit for the data. By observing violin graphs, it becomes evident that models with lower RSME are a better fit for the data. From this, model 3 (bwt_modeltwi) would be the best fit for this data from the models generated. However, the RMSE for each of the models, including 'bwt_modeltwi', are quite high showing that there may be an even better regression model that fits the data.





*To Be Fixed*
```{r}
model_df = 
  crossv_mc(bwt_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

model_df = 
  model_df %>% 
  mutate(
    bwt_model_n   = map(train, ~lm(bwt ~ gaweeks, data = .x))) %>% 
  mutate(
    bwt_modelme_n = map(train, ~lm(bwt ~ blength + gaweeks, data = .x))) %>% 
  mutate(
    bwt_modeltwi_n= map(train, ~lm(bwt ~ bhead + blength + babysex+ bhead*blength + bhead*babysex +                          blength*babysex + bhead*blength*babysex), data = .x))
  mutate(
    rmse_model    = map2_dbl(bwt_model_n, test, ~rmse(model = .x, data = .y)),
    rmse_modelme  = map2_dbl(bwt_modelme_n, test, ~rmse(model = .x, data = .y))),
    rmse_modeltwi = map2_dbl(bwt_modeltwi_n, test, ~rmse(model = .x, data = .y)))
```


```{r}
model_df = 
  crossv_mc(bwt_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

model_df = 
  model_df %>% 
  mutate(
    bwt_model_n   = map(train, ~lm(bwt ~ gaweeks, data = .x)),
    bwt_modelme_n = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    bwt_modeltwi_n= map(train, ~lm(bwt ~ bhead + blength + babysex+ bhead*blength + bhead*babysex +                          blength*babysex + bhead*blength*babysex), data = .x)) %>% 
  mutate(
    rmse_model    = map2_dbl(bwt_model_n, test, ~rmse(model = .x, data = .y)),
    rmse_modelme  = map2_dbl(bwt_modelme_n, test, ~rmse(model = .x, data = .y)),
    rmse_modeltwi = map2_dbl(bwt_modeltwi_n, test, ~rmse(model = .x, data = .y)))
```

```{r}
model_df = 
  model_df %>% 
  mutate(
    bwt_model   = map(train, ~lm(bwt ~ gaweeks, data = .x)),
    bwt_modelme = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    bwt_modeltwi= map(train, ~lm(bwt ~ bhead + blength + babysex+ bhead*blength + bhead*babysex +                          blength*babysex + bhead*blength*babysex), data = .x)) %>% 
  mutate(
    rmse_model    = map2_dbl(bwt_model, test, ~rmse(model = .x, data = .y)),
    rmse_modelme  = map2_dbl(bwt_modelme, test, ~rmse(model = .x, data = .y)),
    rmse_modeltwi = map2_dbl(bwt_modeltwi, test, ~rmse(model = .x, data = .y)))
```

